Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-22 Documentation/manuscript.tex
Manuscript edits.

@@

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named. Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions. A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C. Each form of the survey includes the X block as well as two of the remaining blocks. This leaves the configurations seen in Table \\ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. Note that every block appears in at least one form. By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this. \par

We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.

% \begin{table}[h!]
% 	\centering
% 	\caption{The Three Form PM Design}
% 	\label{tab:table10}
% 	\setlength{\tabcolsep}{1cm}
% 	\begin{tabular}{c|cccc}
% 		\toprule
% 		& \multicolumn{4}{c}{Block} \\
% 		Form & X & A & B & C \\
% 		\midrule
% 		1 & 1 & 1 & 1 & 0 \\
% 		2 & 1 & 1 & 0 & 1 \\
% 		3 & 1 & 0 & 1 & 1 \\
% 		\bottomrule
% 	\end{tabular}
% \end{table}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
\end{figure}

@@

Figure \ref{fig:misslow} is

An important consideration when designing a Split Form survey is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}. On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}. Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}. Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables. We may also wish to consider the cost and burden associated with an item when deciding which block to place it in. For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}. \par

In additon, the number of blocks must be determined. Including more blocks in the design allows further increased missingness \citep{graham2006planned}. For example, consider two groups of researchers. The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each. The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations. Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%. \par

While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks. Inevitably, greater missingness leads to less efficient estimation \citep{rhemtulla2016asymptotic} but there is the added complication as more blocks introduce additional forms. If the second group of researchers in the example, for instance, decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms. For traditional paper surveys, this can make administering the survey difficult. However, for electronic questionaires, where form randomization can be automated, this is not an issue. Often, researchers using electronic surveys will give each participant a random sample of all survey items, in a way treating each item as its own block \citep{silvia2014planned}. Using this method, researchers reap the benefits of increased forms without the difficulty caused by manually building and administering these forms. \par

\subsection{Wave Missingness Design}
\label{sec:1.2}
While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves". Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely. An example of a Wave Missing design is shown in Table \ref{tab:table11} where data is collected monthly over the course of 5 months. However, each participant is only measured at three of these occasions. \par

\begin{table}[b!]
	\centering
	\caption{The Wave Missingness PM Design}
	\label{tab:table11}
	\setlength{\tabcolsep}{0.75cm}
	\begin{tabular}{c|ccccc}
		\toprule
		& \multicolumn{5}{c}{Month} \\
		Participant & 1 & 2 & 3 & 4 & 5 \\
		\midrule
		1 & 1 & 0 & 1 & 0 & 1 \\
		2 & 1 & 1 & 0 & 1 & 0 \\
		3 & 0 & 0 & 1 & 1 & 1 \\
		4 & 1 & 1 & 1 & 0 & 0 \\
		\bottomrule
	\end{tabular}
\end{table}

Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}. Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}. For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years. Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two. Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information. By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study. The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave. \par

\begin{table}[t!]
	\centering
	\caption{Cohort Sequential Design}
	\label{tab:table12}
	\setlength{\tabcolsep}{0.5cm}
	\begin{tabular}{c|cccccc}
		\toprule
		& \multicolumn{6}{c}{Age} \\
		Participant & 10 & 11 & 12 & 13 & 14 & 15 \\
		\midrule
		1 & 1 & 1 & 1 & 1 & 0 & 0\\
		2 & 0 & 1 & 1 & 1 & 1 & 0\\
		3 & 0 & 0 & 1 & 1 & 1 & 1\\
		\bottomrule
	\end{tabular}
\end{table}

Developmental time-lag models \citep{mcardle1997expanding} also make use of the Wave Missingness structure. As shown in Table \ref{tab:table13}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values. Under this framework they impute these missing values and estimate growth curve models. Estimating this type of model would normally require measuring participants at many time points. However, under the Wave Missingness design this is accomplished with only two measurement occasions per participant. These designs exemplify how useful the Wave Missingness structure is in accelerating longitudinal studies. \par

\begin{table}[b!]
	\centering
	\caption{Developmental Time-Lag Setup}
	\label{tab:table13}
	\setlength{\tabcolsep}{0.75cm}
	\begin{tabular}{c|cccc}
		\toprule
		& \multicolumn{4}{c}{Wave} \\
		Participant & 1 & 2 & 3 & 4 \\
		\midrule
		1 & 1 & 1 & 0 & 0 \\
		2 & 1 & 0 & 1 & 0 \\
		3 & 1 & 0 & 0 & 1 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120. The rest of the simulation process was carried out as before. As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient. Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. \par
\subsubsection{High Time Effect}
In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased. This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. Decreasing the other variables effects ensured that time has a disproportionate effect without this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

\section{Results}
\label{sec:3}
\subsection{Primary Simulation}
\label{sec:3.1}
The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$. The effects of the variables here are comparable to those found in the original dataset. This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design. Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}. Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{\begin{tabular}{l|l|l|r|r|r|r|r|r}
\hline
Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
\hline
 &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
\cline{3-9}
 &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
\cline{3-9}
 &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
\cline{3-9}
 &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
\cline{1-9}
 &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
\cline{3-9}
 &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
\cline{3-9}
 &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
\cline{2-9}
 &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
\cline{3-9}
 &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
\cline{1-9}
 &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
\cline{3-9}
 &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
\cline{3-9}
 &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
\cline{3-9}
 &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
\cline{2-9}
 &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
\cline{3-9}
 &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
\cline{3-9}
 &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
\hline
\end{tabular}}
\end{table}

@@

Towards the bottom of Table \ref{tab:table3}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness. Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.  Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates. \par

\subsection{Increased Sample Size}
\label{sec:3.2}
In the next simulation scenario the sample size was increased to 120 participants. All parameter values were held the same as in the original simulation. Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design. \par

>>>>

% Predefine some figures

@@

\raggedbottom

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named. Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions. How these subsets are chosen varies. A common form setup is three-form Block Design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C. Each form of the survey includes the X block as well as two of the remaining blocks. A participant is then given a different form each day of the study. Designing the forms in this manner allows researchers to estimate the relationship between any chosen items, regardless of their blocks. For example, this allows the relationship between an item in block A and another in block C to be estimated and examined. \par

An important consideration here is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}. On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}. Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}. While this approach provides researchers more freedom when forming the surveys, the puzzle of question distribution introduces new concerns. When the question groupings are not obvious, pilot studies may be necessary to determine the predictive potential of and relationships between variables. The cost and burden associated with an item must also be considered when deciding which block to place it in. For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}. \par

In addition, the number of blocks must be determined. Including more blocks in the design allows further increased missingness \citep{graham2006planned}. While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks. As more blocks are added, the number of possible forms increases. For example, consider two research teams. The first team divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey. The second uses an X-block and nine others with 10\% of the items each. If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 \textbf{(28? 8 choose 2?)} total forms while the first team can proceed with 3. \textbf{This is all assuming that the blocks represent the optimal question grouping. If this is not known, to account for possible relationships and correlation between questions, the teams would need to consider all possible blocks and create forms for every block configuration. For a 7 question survey, with any one question X block and the other 6 split into three blocks, there are 75 possible block configurations. For each configuration, there are 3 possible forms. So, a team would need to consider 225 different forms. Instead of creating 225 distinct forms, a research team can follow a alternative Split Form method.} \par

\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $n$ questions and then randomly excluding $k$ questions on each day. In a way treating each item as its own block \citep{silvia2014planned}. This is simple in theory, but for traditional paper surveys this is very difficult to execute. Fortunately, recent technological advances have made the use of electronic questionaires more readily accessible. In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.} Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms. \par

\subsection{Wave Missingness Design}
\label{sec:1.2}
While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves". Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely. An example of a Wave Missing design is shown in Figure \ref{fig:formillustration} where data is collected monthly over the course of 5 months. However, each participant is only measured at three of these occasions. \par

Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}. Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}. For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years. Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two. Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information. By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study. The setup of this type of study is demonstrated in Table \ref{tab:cohort}, where "1" and "0" respectively indicate an included and excluded wave. \par

\begin{table}[H]
	\centering
	\caption{Cohort Sequential Design}
	\label{tab:cohort}
	\setlength{\tabcolsep}{0.5cm}
	\begin{tabular}{c|cccccc}
		\toprule
		& \multicolumn{6}{c}{Age} \\
		Participant & 10 & 11 & 12 & 13 & 14 & 15 \\
		\midrule
		1 & 1 & 1 & 1 & 1 & 0 & 0\\
		2 & 0 & 1 & 1 & 1 & 1 & 0\\
		3 & 0 & 0 & 1 & 1 & 1 & 1\\
		\bottomrule
	\end{tabular}
\end{table}

Developmental time-lag models \citep{mcardle1997expanding} use the Wave Missingness structure, as well. As shown in Table \ref{tab:devtimelag}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values. Under this framework they impute these missing values and estimate growth curve models. Estimating this type of model would normally require measuring participants at many time points. However, under the Wave Missingness design this is accomplished with only two measurement occasions per participant. These designs exemplify how useful the Wave Missingness structure is in accelerating longitudinal studies. \par

\begin{table}[H]
	\centering
	\caption{Developmental Time-Lag Setup}
	\label{tab:devtimelag}
	\setlength{\tabcolsep}{0.75cm}
	\begin{tabular}{c|cccc}
		\toprule
		& \multicolumn{4}{c}{Wave} \\
		Participant & 1 & 2 & 3 & 4 \\
		\midrule
		1 & 1 & 1 & 0 & 0 \\
		2 & 1 & 0 & 1 & 0 \\
		3 & 1 & 0 & 0 & 1 \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Altered Split Form}

The Split Form planned missingness method can be modified to include the benefits of complete cases seen in Wave Missingness in what may be called Altered Split Form. In this method, the researcher asks participants all questions on the first $n$ days of the study. Thereafter, the survey design reverts to regular Split Form. This method allows the researcher to collect $n$ complete cases from each participant, aiding in the imputation process after surveys are administered. Altered Split Form, and the other planned missingness methods, is illustrated in Figure \ref{fig:formillustration} below.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
\includegraphics[width=\maxwidth]{figure/formillustration-1} \caption[Low missingness]{Low missingness}\label{fig:formillustration}
\end{figure}

@@

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120. The rest of the simulation process was carried out as before. As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient. Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. To investigate this, the correlation of the variables was scaled by 0.5.\par
\subsubsection{High Time Effect}
In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0$, $\beta_1$, $\beta_2$, and $\beta_3$ to -4.56, 0.14, 0.32, and 0.01 respectively. Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased. This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. Decreasing the other variables effects ensured that time has a disproportionate effect without this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

\section{Results}
\label{sec:3}
\subsection{Primary Simulation}
\label{sec:3.1}
The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.28$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.01$. The effects of the variables here are comparable to those found in the original dataset. This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design. Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}. Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.

Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}. \textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]

\caption{\label{tab:primary}Primary Results (N = 60)}
\centering
\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
\hline
Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
\hline
 &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
\cline{3-9}
 &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
\cline{3-9}
 &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
\cline{3-9}
 &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
\cline{1-9}
 &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
\cline{3-9}
 &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
\cline{3-9}
 &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
\cline{2-9}
 &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
\cline{3-9}
 &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
\cline{1-9}
 &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
\cline{3-9}
 &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
\cline{3-9}
 &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
\cline{3-9}
 &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
\cline{2-9}
 &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
\cline{3-9}
 &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
\cline{3-9}
 &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
\hline
\end{tabular}}
\end{table}

@@

Towards the bottom of Table \ref{tab:primary}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness. Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.  Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates. \par

\subsection{Increased Sample Size}
\label{sec:3.2}
In the next simulation scenario the sample size was increased to 120 participants. All parameter values were held the same as in the original simulation. Table \ref{tab:prelim} \textbf{not here yet}, again, contains the results of the analysis before applying any PM design. The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:sampsize}. \par

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
